\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{xr-hyper}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments.text}
\input{../Common.text}

\externaldocument{../SRS/SRS}

\renewcommand{\progname}{Integrating NCRF into existing pipeline}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{Yanyu Wu}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
April 20, 2026 & 1.3 & Revisions based on professor's feedback\\
Mar 25, 2026 & 1.2 & Address additional VnV peer review issues\\
Mar 25, 2026 & 1.1 & Address peer review issues for VnV Plan\\
Feb 11 & 1.0 & Initial draft\\
\bottomrule
\end{tabularx}

% ~\\
% \wss{The intention of the VnV plan is to increase confidence in the software.
% However, this does not mean listing every verification and validation technique
% that has ever been devised.  The VnV plan should also be a \textbf{feasible}
% plan. Execution of the plan should be possible with the time and team available.
% If the full plan cannot be completed during the time available, it can either be
% modified to ``fake it'', or a better solution is to add a section describing
% what work has been completed and what work is still planned for the future.}

% \wss{The VnV plan is typically started after the requirements stage, but before
% the design stage.  This means that the sections related to unit testing cannot
% initially be completed.  The sections will be filled in after the design stage
% is complete.  the final version of the VnV plan should have all sections filled
% in.}

\newpage

\tableofcontents

\listoftables
% \wss{Remove this section if it isn't needed}

% \listoffigures
% \wss{Remove this section if it isn't needed}

\newpage

\section{Symbols, Abbreviations, and Acronyms}

% \renewcommand{\arraystretch}{1.2}
% \begin{tabular}{l l} 
%   \toprule		
%   \textbf{symbol} & \textbf{description}\\
%   \midrule 
%   T & Test\\
%   \bottomrule
% \end{tabular}\\

% \wss{symbols, abbreviations, or acronyms --- you can simply reference the SRS
%   \citep{SRS} tables, if appropriate}

% \wss{Remove this section if it isn't needed}

The definition of symbols, abbreviations and acronyms is as same as those in my SRS documents.

\newpage

\pagenumbering{arabic}

This document provides an introductory blurb and roadmap of the NCRF pipeline Verification and Validation plan.

\section{General Information}

\subsection{Summary}

% \wss{Say what software is being tested.  Give its name and a brief overview of
%   its general functions.}
Integrating NCRF into existing pipeline is intended to solve the error propagation issue of
traditional TRF-based pipeline. Using NCRF could allow spatial and temporal response
properties to be estimated jointly, instead of sequentially.
\subsection{Objectives}
\textbf{Primary Objectives}
\begin{itemize}
  \item Build confidence that the NCRF integration satisfies the SRS functional requirements.
  \item Verify numerical correctness on small, controlled datasets by matching expected outputs within defined tolerances.
  \item Demonstrate reproducibility of results across repeated runs with fixed seeds and documented configurations.
  \item Guarantee key non-functional requirements (e.g., reliability, traceability).
\end{itemize}
\textbf{Out of Scope}
\begin{itemize}
  \item Internal correctness or performance of third-party libraries (e.g., Eelbrain, MNE); assume they are already verified by their maintainers.
  \item Large-scale performance and scalability benchmarking on very large datasets.
\end{itemize}
% \wss{State what is intended to be accomplished.  The objective will be around
%   the qualities that are most important for your project.  You might have
%   something like: ``build confidence in the software correctness,''
%   ``demonstrate adequate usability.'' etc.  You won't list all of the qualities,
%   just those that are most important.}

% \wss{You should also list the objectives that are out of scope.  You don't have 
% the resources to do everything, so what will you be leaving out.  For instance, 
% if you are not going to verify the quality of usability, state this.  It is also 
% worthwhile to justify why the objectives are left out.}

% \wss{The objectives are important because they highlight that you are aware of 
% limitations in your resources for verification and validation.  You can't do everything, 
% so what are you going to prioritize?  As an example, if your system depends on an 
% external library, you can explicitly state that you will assume that external library 
% has already been verified by its implementation team.}

\subsection{Extras}

% \wss{Summarize the extras (if any) that were tackled by this project.  Extras
% can include usability testing, code walkthroughs, user documentation, formal
% proof, GenderMag personas, Design Thinking, etc.  Extras should have already
% been approved by the course instructor as included in your problem statement.
% You can use a pull request to update your extras (in TeamComposition.csv or
% Repos.csv) if your plan changes as a result of the VnV planning exercise.}
Two project extras are planned and were declared at the start of the course:
\textbf{User Manual} and \textbf{Code Walkthrough}. 

The User Manual will provide task-oriented guidance (installation, input preparation, running the pipeline,
and interpreting outputs) and will be validated through checklist-based review
for clarity, completeness, and consistency with the SRS and system behavior. The

Code Walkthrough will be a structured inspection session using a checklist to
verify coding standards, traceability from requirements to implementation, and
consistency with the architecture and detailed design documents. Findings from
both activities will be recorded as actionable issues and tracked to resolution.

\subsection{Relevant Documentation}

% \wss{Reference relevant documentation.  This will definitely include your SRS
%   and your other project documents (design documents, like MG, MIS, etc).  You
%   can include these even before they are written, since by the time the project
%   is done, they will be written.  You can create BibTeX entries for your
%   documents and within those entries include a hyperlink to the documents.}

The Software Requirements Specification (SRS) is the primary source for
verification targets; all test cases and traceability links originate from it
(\href{../SRS/SRS.tex}{SRS}).

The Module Guide (MG) defines the system
decomposition and responsibilities used to plan design-level reviews and
coverage (\href{../Design/SoftArchitecture/MG.tex}{MG}).

The Module Interface Specification (MIS) provides detailed module interfaces and expected behaviors
to support unit-level verification (\href{../Design/SoftDetailedDes/MIS.tex}{MIS}).

% \citet{SRS}

% \wss{Don't just list the other documents.  You should explain why they are relevant and 
% how they relate to your VnV efforts.}
\newpage

\section{Plan}
This section provides a roadmap of the verification and validation activities planned for the project.
% \wss{Introduce this section.  You can provide a roadmap of the sections to
%   come.}


\subsection{Verification and Validation Team}

\begin{table}[h!]
\centering
\begin{tabularx}{\textwidth}{p{0.18\textwidth} p{0.22\textwidth} X}
\toprule
\textbf{Member} & \textbf{Role} & \textbf{Responsibilities} \\
\midrule
Yanyu Wu & Developer\&  V\&V Lead & Owns the V\&V plan, executes verification activities, and documents results and issues. \\
Dr.Brodbeck & Reviewer & Provides high-level guidance on direction and priorities. \\
Dr.Smith & Course Instructor & Provides feedback on the V\&V plan and documentation. \\
Zhangwenchi Li & Domain Expert & Conducts code review and provides domain feedback on code and documentation. \\
\bottomrule
\end{tabularx}
\caption{Verification and Validation Team}
\label{tab:vv_team}
\end{table}

% \wss{Your teammates.  Maybe your supervisor.
%   You should do more than list names.  You should say what each person's role is
%   for the project's verification.  A table is a good way to summarize this information.}

\subsection{SRS Verification}

% \wss{List any approaches you intend to use for SRS verification.  This may
%   include ad hoc feedback from reviewers, like your classmates (like your
%   primary reviewer), or you may plan for something more rigorous/systematic.}
%
% \wss{If you have a supervisor for the project, you shouldn't just say they will
% read over the SRS.  You should explain your structured approach to the review.
% Will you have a meeting?  What will you present?  What questions will you ask?
% Will you give them instructions for a task-based inspection?  Will you use your
% issue tracker?}
%
% \wss{Maybe create an SRS checklist?}
SRS verification will be done through a structured review and a requirements
checklist:
\begin{itemize}
  \item Domain expert review for scientific validity and consistency with NCRF pipeline goals.
  \item Supervisor review for clarity, completeness, and alignment with project scope.
  \item Developer self-check to ensure functional and non-functional requirements are specific, testable, and traceable.
  \item SRS checklist inspection using \href{../Checklists/SRS-Checklist.tex}{SRS-Checklist} to ensure required sections and quality criteria are covered.
\end{itemize}

\subsection{Design Verification}

% \wss{Plans for design verification}

% \wss{The review will include reviews by your classmates}
%
% \wss{Create a checklists?}
Design verification will combine structured peer review and checklist-based inspection:
\begin{itemize}
  \item Classmate / peer design review: scheduled walkthrough sessions where classmates provide feedback on the design documents (MG and MIS).
  \item Design checklists: ensure each SRS requirement is addressed at the design level, with checks for modularity, clarity, and traceability to requirements.
\end{itemize}

\subsection{Verification and Validation Plan Verification}

% \wss{The verification and validation plan is an artifact that should also be
% verified.  Techniques for this include review and mutation testing.}
%
% \wss{The review will include reviews by your classmates}
%
% \wss{Create a checklists?}
The V\&V plan will be verified to ensure it is complete, feasible, and aligned
with the SRS:
\begin{itemize}
  \item Peer review to check clarity, coverage, and feasibility of the planned activities.
  \item V\&V checklist inspection to ensure required sections and details are present.
  \item Traceability spot-check to confirm each SRS requirement has at least one planned verification method.
\end{itemize}

\subsection{Implementation Verification}

% \wss{You should at least point to the tests listed in this document and the unit
%   testing plan.}
%
% \wss{In this section you would also give any details of any plans for static
%   verification of the implementation.  Potential techniques include code
%   walkthroughs, code inspection, static analyzers, etc.}
%
% \wss{The final class presentation in CAS 741 could be used as a code
% walkthrough.  There is also a possibility of using the final presentation (in
% CAS741) for a partial usability survey.}
Implementation verification will focus on test execution, requirements coverage,
and inspection:
\begin{itemize}
  \item Execute planned test cases (unit and system-level) and record results against expected outputs.
  \item Verify coverage by checking each SRS requirement is implemented and has at least one corresponding test.
  \item Conduct code walkthroughs to inspect critical logic, edge cases, and consistency with the design (MG/MIS).
\end{itemize}

\subsection{Automated Testing and Verification Tools}

% \wss{What tools are you using for automated testing.  Likely a unit testing
%   framework and maybe a profiling tool, like ValGrind.  Other possible tools
%   include a static analyzer, make, continuous integration tools, test coverage
%   tools, etc.  Explain your plans for summarizing code coverage metrics.
%   Linters are another important class of tools.  For the programming language
%   you select, you should look at the available linters.  There may also be tools
%   that verify that coding standards have been respected, like flake9 for
%   Python.}

% \wss{If you have already done this in the development plan, you can point to
% that document.}

% \wss{The details of this section will likely evolve as you get closer to the
%   implementation.}
Automated verification will use a small set of standard Python tools and CI:
\begin{itemize}
  \item Continuous Integration (CI) to run tests and checks on each update to the repository.
  \item Unit testing with `pytest` for functional correctness of modules and utilities.
  \item Coverage tracking with `Coverage.py` to summarize test coverage.
\end{itemize}

\subsection{Software Validation}
Not applicable. This project integrates an existing NCRF model into the pipeline rather than developing a new scientific model. Validation of the underlying model is out of scope and is assumed to be covered by the original NCRF publications and reference implementations.

% \wss{If there is any external data that can be used for validation, you should
%   point to it here.  If there are no plans for validation, you should state that
%   here.}

% \wss{You might want to use review sessions with the stakeholder to check that
% the requirements document captures the right requirements.  Maybe task based
% inspection?}

% \wss{For those capstone teams with an external supervisor, the Rev 0 demo should 
% be used as an opportunity to validate the requirements.  You should plan on 
% demonstrating your project to your supervisor shortly after the scheduled Rev 0 demo.  
% The feedback from your supervisor will be very useful for improving your project.}

% \wss{For teams without an external supervisor, user testing can serve the same purpose 
% as a Rev 0 demo for the supervisor.}

% \wss{This section might reference back to the SRS verification section.}

\section{System Tests}
This section describes the system tests planned for the project.
% \wss{There should be text between all headings, even if it is just a roadmap of
% the contents of the subsections.}

\subsection{Tests for Functional Requirements}
This sections defines the test cases for key funtional areas of Integrating NCRF into existing pipeline. The goal for the test cases are checking the project correctly calculated the result using NCRF and the functions are be integrated into the existing pipeline correctly.

The test cases are derived from the functional requirements in the Software Requirements Specification (SRS).

% \wss{Subsets of the tests may be in related, so this section is divided into
%   different areas.  If there are no identifiable subsets for the tests, this
%   level of document structure can be removed.}

% \wss{Include a blurb here to explain why the subsections below
%   cover the requirements.  References to the SRS would be good here.}
The subsections below map directly to the SRS functional requirements:
input handling (\hyperref[R-Inputs]{R-Inputs}), NCRF computation (\hyperref[R-Calculate]{R-Calculate}), and
output generation for downstream analysis (\hyperref[R-Output]{R-Output}). Each test area
is designed to verify that the implemented pipeline satisfies these specific
requirements.

% \wss{It would be nice to have a blurb here to explain why the subsections below
%   cover the requirements.  References to the SRS would be good here.  If a section
%   covers tests for input constraints, you should reference the data constraints
%   table in the SRS.}

\subsubsection{Input Handling and API Selection (\hyperref[R-Inputs]{R-Inputs})}
This area verifies that the pipeline accepts required inputs and exposes an API for using NCRF estimator.
		
\paragraph{Input and Estimator Selection}

\begin{enumerate}

\item{FR-INPUT-01\\}

\textbf{Control:} Automatic
					
\textbf{Initial State:} Test data is staged with BIDS MEG recordings under
\texttt{\textasciitilde/Data/BIDS} (for example \texttt{sub-01}, task
\texttt{Appleseed}) and predictor files exist in
\texttt{<deriv-dir>/predictors/}, including
\texttt{Appleseed\textasciitilde acoustic\_envelop.pickle} and
\texttt{Tone\textasciitilde acoustic\_envelop.pickle}.
					
\textbf{Input:} Stimulus feature signal $e(t)$ is the acoustic envelope
(\texttt{NDVar}) loaded from
\texttt{<deriv-dir>/predictors/Appleseed\textasciitilde acoustic\_envelop.pickle};
neural input is MEG data from BIDS subject \texttt{sub-01} (task
\texttt{Appleseed}); call \texttt{load\_trf(estimator="ncrf")}.
					
\textbf{Output:} The NCRF pipeline is invoked without input/parameter errors; data and parameters are accepted.

\textbf{Test Case Derivation:} \hyperref[R-Inputs]{R-Inputs} requires the system to accept $e(t)$ as input.
					
\textbf{How Test Will Be Performed:} Run with subject \texttt{sub-01}, task
\texttt{Appleseed}, and the predictor file
\texttt{Appleseed\textasciitilde acoustic\_envelop.pickle}; verify logs show the
NCRF path is selected and no input/parameter validation error is raised.
					
\item{FR-API-02\\}

\textbf{Control:} Automatic
					
\textbf{Initial State:} Same as FR-INPUT-01.
					
\textbf{Input:} Call \texttt{load\_trf(estimator="unknown")}.
					
\textbf{Output:} A clear error is raised indicating invalid estimator and listing supported options.

\textbf{Test Case Derivation:} The API must validate estimator selection to prevent invalid execution paths.

\textbf{How Test Will Be Performed:} Invoke the call and verify the error message and exit behavior.

\item{FR-API-03\\}

\textbf{Control:} Automatic
					
\textbf{Initial State:} Existing TRF workflow configuration.
					
\textbf{Input:} Call \texttt{load\_trf()} without specifying estimator.
					
\textbf{Output:} Default (boosting) behavior is preserved; no regression in baseline workflow.

\textbf{Test Case Derivation:} Check API unification without breaking existing TRF usage.

\textbf{How Test Will Be Performed:} Run one fixed baseline configuration (same subject, epoch, predictor, \texttt{tstart/tstop}, and sampling rate) once with legacy call style and once with \texttt{load\_trf()} default estimator. Pass criteria: (1) both runs complete without exception, (2) both return \texttt{BoostingResult}, (3) output dimensions match exactly, and (4) relative error of key numeric outputs (\texttt{r} and TRF coefficients) is $\leq 10^{-6}$.

\end{enumerate}

\subsubsection{NCRF Computation (\hyperref[R-Calculate]{R-Calculate})}
This area verifies that NCRF estimation executes and produces valid outputs.

\paragraph{NCRF Execution Sanity}

\begin{enumerate}

\item{FR-CALC-01\\}

\textbf{Control:} Automatic

\textbf{Initial State:} Small, controlled dataset with fixed configuration.

\textbf{Input:} Acoustic-envelope predictor $e(t)$ loaded from \texttt{<deriv-dir>/predictors/Appleseed\textasciitilde acoustic\_envelop.pickle}, MEG data for BIDS subject \texttt{sub-01} and task \texttt{Appleseed}, \texttt{tstart=0}, \texttt{tstop=0.5}, sampling rate \SI{100}{Hz}, and \texttt{NCRFEstimator(mu=0.1, n\_iter=100)}.

\textbf{Output:} NCRF result object is created and contains source-current output $j_{m,t}$ and coefficient tensor $\tau_{m,i,\ell}$ with one predictor axis (\(i=1\)), non-zero source and lag dimensions, and only finite values (no NaN/Inf).

\textbf{Test Case Derivation:} \hyperref[R-Calculate]{R-Calculate} requires computation of source-level neural current estimates.

\textbf{How Test Will Be Performed:} Run NCRF once with the fixed configuration above and verify that the returned object contains both $j_{m,t}$ and $\tau_{m,i,\ell}$, that the predictor dimension equals 1, and that all numeric entries are finite.

\item{FR-CALC-02\\}

\textbf{Control:} Automatic

\textbf{Initial State:} Same as FR-CALC-01 with fixed random seed.

\textbf{Input:} Same predictor file, subject, task, and NCRF configuration as FR-CALC-01, with a fixed random seed and unchanged runtime environment.

\textbf{Output:} Two NCRF runs produce matching output shapes and numerically consistent $\tau_{m,i,\ell}$ values with relative error $\leq 10^{-6}$ under the same fixed configuration.

\textbf{Test Case Derivation:} Supports reproducibility expectations aligned with NFR1 while validating computation.

\textbf{How Test Will Be Performed:} Execute the same NCRF call twice and compare the returned $\tau_{m,i,\ell}$ tensors; the test passes if shapes are identical and relative error is $\leq 10^{-6}$.

\end{enumerate}

\subsubsection{Output Generation and Downstream Use (\hyperref[R-Output]{R-Output})}
This area verifies output content and compatibility with downstream analysis.

\paragraph{Output Format and Integration}

\begin{enumerate}

\item{FR-OUT-01\\}

\textbf{Control:} Automatic

\textbf{Initial State:} Successful NCRF computation completed.

\textbf{Input:} NCRF output objects/files.

\textbf{Output:} Outputs include $j_{m,t}$ and $\tau_{m,i,\ell}$ in the expected structure and format.

\textbf{Test Case Derivation:} \hyperref[R-Output]{R-Output} requires both outputs in a format suitable for downstream analysis.

\textbf{How Test Will Be Performed:} Inspect output fields and validate metadata/shape consistency.

\item{FR-OUT-02\\}

\textbf{Control:} Automatic

\textbf{Initial State:} Outputs from FR-OUT-01 available.

\textbf{Input:} Load NCRF outputs into the existing downstream pipeline step.

\textbf{Output:} Downstream analysis successfully loads and processes the outputs without format errors.

\textbf{Test Case Derivation:} \hyperref[R-Output]{R-Output} requires interoperability with the existing pipeline.

\textbf{How Test Will Be Performed:} Execute downstream loading script and verify completion.

\end{enumerate}

...

\subsection{Tests for Nonfunctional Requirements}

% \wss{The nonfunctional requirements for accuracy will likely just reference the
%   appropriate functional tests from above.  The test cases should mention
%   reporting the relative error for these tests.  Not all projects will
%   necessarily have nonfunctional requirements related to accuracy.}

% \wss{For some nonfunctional tests, you won't be setting a target threshold for
% passing the test, but rather describing the experiment you will do to measure
% the quality for different inputs.  For instance, you could measure speed versus
% the problem size.  The output of the test isn't pass/fail, but rather a summary
% table or graph.}

% \wss{Tests related to usability could include conducting a usability test and
%   survey.  The survey will be in the Appendix.}

% \wss{Static tests, review, inspections, and walkthroughs, will not follow the
% format for the tests given below.}

% \wss{If you introduce static tests in your plan, you need to provide details.
% How will they be done?  In cases like code (or document) walkthroughs, who will
% be involved? Be specific.}

\subsubsection{Accuracy and Reproducibility (NFR1)}
		
\paragraph{Numerical Stability Against Documented Baseline}

\begin{enumerate}

\item{NFR-ACC-01\\}

Type: Dynamic, Automatic
					
\textbf{Initial State:} A documented baseline NCRF run is available for one fixed dataset, predictor file, and parameter configuration.
					
\textbf{Input}/Condition: Run NCRF on the same fixed dataset and predictor configuration used to create the documented baseline.
					
\textbf{Output}/Result: Output matches the documented baseline within a relative error tolerance of $1\times 10^{-3}$ using the same output tensor comparison method.
					
\textbf{How Test Will Be Performed:} Compare $j_{m,t}$ and $\tau_{m,i,\ell}$ from the current run to the stored baseline run under the same configuration and report relative error metrics.
					
\item{NFR-ACC-02\\}

Type: Dynamic, Automatic
					
\textbf{Initial State:} Fixed random seed and configuration.
					
\textbf{Input}/Condition: Repeat the same NCRF estimation twice with the same predictor file, subject, parameter configuration, and fixed random seed.
					
\textbf{Output}/Result: The NCRF coefficient tensor $\tau_{m,i,\ell}$ from both runs has identical shape and relative error $\leq 10^{-6}$; if $j_{m,t}$ is exposed by the result object, it must also have identical shape and relative error $\leq 10^{-6}$.
					
\textbf{How Test Will Be Performed:} Execute the same NCRF call twice, compute relative error separately for $\tau_{m,i,\ell}$ (and for $j_{m,t}$ if present), and report both the tensor shape comparison and the numeric error values.

\end{enumerate}

\subsubsection{Maintainability (NFR2)}
		
\paragraph{Modularity and Code Structure Review}

\begin{enumerate}

\item{NFR-MAINT-01\\}

Type: Static, Manual
					
\textbf{Initial State:} MG/MIS and codebase are available for review.
					
\textbf{Input}/Condition: Inspect module structure and interfaces for separation of concerns.
					
\textbf{Output}/Result: NCRF integration is localized to well-defined modules, with minimal changes to unrelated code.
					
\textbf{How Test Will Be Performed:} Conduct a manual design review against the module hierarchy and decomposition in \texttt{docs/Design/SoftArchitecture/MG.tex} and the interface specifications in \texttt{docs/Design/SoftDetailedDes/MIS.tex}, especially the Input Preprocessing, Estimator Resolution, and TRF Computation modules. The review is performed by the project author together with at least one peer reviewer; identified issues are recorded in the review notes and re-checked after revisions.

\end{enumerate}

\subsubsection{Portability (NFR3)}
		
\paragraph{Cross-Platform Execution}

\begin{enumerate}

\item{NFR-PORT-01\\}

Type: Dynamic, Automatic
					
\textbf{Initial State:} Supported environments available (macOS, Windows, Linux) or CI matrix configured.
					
\textbf{Input}/Condition: Run a minimal NCRF workflow on each platform.
					
\textbf{Output}/Result: The pipeline executes without platform-specific errors.
					
\textbf{How Test Will Be Performed:} Execute automated tests in CI (or local runs) and record pass/fail on each OS.

\end{enumerate}

\subsection{Traceability Between Test Cases and Requirements}

% \wss{Provide a table that shows which test cases are supporting which
%   requirements.}
This table provides a mapping between the requirements in the SRS and the test cases defined in this VnV plan.
Table~\ref{tab:traceability} summarizes traceability between requirements in the
SRS and the test cases defined in this VnV plan.

\begin{table}[h!]
\centering
\begin{tabularx}{\textwidth}{p{0.28\textwidth} X}
\toprule
\textbf{Requirement} & \textbf{Test Cases} \\
\midrule
\hyperref[R-Inputs]{R-Inputs}  & FR-INPUT-01, FR-API-02, FR-API-03 \\
\hyperref[R-Calculate]{R-Calculate} & FR-CALC-01, FR-CALC-02 \\
\hyperref[R-Output]{R-Output} & FR-OUT-01, FR-OUT-02 \\
NFR1 (Accuracy) & NFR-ACC-01, NFR-ACC-02 \\
NFR2 (Maintainability) & NFR-MAINT-01 \\
NFR3 (Portability) & NFR-PORT-01 \\
\bottomrule
\end{tabularx}
\caption{Traceability Between Requirements and Test Cases}
\label{tab:traceability}
\end{table}


\section{Unit Test Description}

This section defines the planned unit testing strategy based on the completed MIS. The unit tests are selected from the access programs and semantics specified in \href{../Design/SoftDetailedDes/MIS.tex}{MIS.tex}. The goal is not to re-test third-party scientific libraries, but to verify that the project integration code resolves estimators correctly, prepares predictor/epoch data according to the documented interfaces, dispatches the correct analysis method, and handles cache/output behavior consistently.

The unit tests will be implemented with \texttt{pytest}. Tests will use small fixtures, temporary directories, and mocks/stubs for expensive external calls. Full NCRF fitting on the Appleseed dataset is treated as system/integration testing, not unit testing, because it depends on external data, forward/covariance files, Eelbrain, MNE, and the \texttt{neuro-currentRF} backend.

\subsection{Unit Testing Scope}

The unit testing scope is determined by the four MIS modules:
\begin{itemize}
  \item M1 Data Loading Module: verify filesystem and serialization behavior at the interface boundary.
  \item M2 Data Preprocessing Module: verify epoch loading contracts and predictor-column insertion behavior.
  \item M3 Estimator Resolution Module: verify estimator-key lookup, invalid-estimator handling, and estimator option merging.
  \item M4 TRF Computation Module: verify cache behavior and dispatch to the correct analysis method based on estimator selection.
\end{itemize}

The following are outside the unit testing scope:
\begin{itemize}
  \item Numerical correctness of Eelbrain, MNE, and \texttt{neuro-currentRF}; these are third-party libraries and are assumed to be verified by their maintainers.
  \item Full Appleseed BIDS execution and full NCRF model fitting; these are covered by system tests because they require large external data and scientific backend dependencies.
  \item Operating-system file I/O internals; unit tests only verify that the project calls these interfaces correctly and handles expected exceptions.
\end{itemize}

\subsection{Tests for Functional Requirements}

\subsubsection{M1: Data Loading Module}

The Data Loading Module is specified in the Hardware-Hiding Module section of the MIS. Unit tests for this module focus on the documented access routines \texttt{RawSource.\_load} and \texttt{save.pickle}. These tests support R-Inputs and R-Output by checking that raw recordings and serialized artifacts are handled through the expected filesystem interfaces.

\begin{enumerate}

\item{UT-DL-01: Raw recording load succeeds\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A small valid raw-recording fixture or mocked MNE reader is available.

\textbf{Input:} \texttt{subject="sub-test"}, a valid recording path, and \texttt{preload=False}.

\textbf{Output:} \texttt{RawSource.\_load} returns a raw data object and does not raise an exception.

\textbf{Test Case Derivation:} The MIS states that \texttt{RawSource.\_load} returns an MNE \texttt{Raw} object loaded from the resolved recording path.

\textbf{How Test Will Be Performed:} Use \texttt{pytest} with a fixture or mocked MNE reader. Assert that the returned object has the expected raw-object interface and that the reader is called with the resolved recording path.

\item{UT-DL-02: Raw recording load reports missing file\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} No file exists at the requested recording path.

\textbf{Input:} \texttt{subject="sub-test"}, a missing recording path, and \texttt{preload=False}.

\textbf{Output:} \texttt{FileNotFoundError} or an equivalent reader I/O error is raised.

\textbf{Test Case Derivation:} The MIS lists \texttt{FileNotFoundError} and \texttt{OSError} as exceptions for missing or unreadable raw recordings.

\textbf{How Test Will Be Performed:} Use a temporary directory and request a nonexistent file. Assert that the documented exception type is raised.

\item{UT-DL-03: Pickle output is written to disk\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A temporary output directory exists.

\textbf{Input:} A small serializable Python object and destination path \texttt{tmp/results.pickle}.

\textbf{Output:} \texttt{save.pickle} returns \texttt{None}, creates the pickle file, and the object can be loaded back with matching content.

\textbf{Test Case Derivation:} The MIS states that \texttt{save.pickle} writes a serialized object to disk for cache/results reuse.

\textbf{How Test Will Be Performed:} Use \texttt{pytest}'s \texttt{tmp\_path}; write a small dictionary; assert file existence and round-trip equality.

\end{enumerate}

\subsubsection{M2: Data Preprocessing Module}

The Data Preprocessing Module is specified in the Data Preprocessing Module section of the MIS. Unit tests for this module verify \texttt{load\_epochs} and \texttt{add\_predictor}, focusing on data-shape contracts, predictor naming, in-place behavior, and invalid predictor handling.

\begin{enumerate}

\item{UT-DP-01: Epoch loading returns dataset with response and metadata\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A small experiment fixture or mocked epoch loader is configured with one subject, one task, and a valid sampling rate.

\textbf{Input:} \texttt{samplingrate=100}, \texttt{data="meg"}, and \texttt{interpolate\_bads=False}.

\textbf{Output:} \texttt{load\_epochs} returns a \texttt{Dataset} containing a response variable, event/stimulus metadata, and a time axis compatible with the requested sampling rate.

\textbf{Test Case Derivation:} The MIS states that \texttt{load\_epochs} returns an epoch dataset containing response data, event metadata, and a consistent time axis.

\textbf{How Test Will Be Performed:} Mock the lower-level Eelbrain epoch loader or use a minimal fixture. Assert that required dataset keys exist and that the time-axis sampling rate matches the requested value.

\item{UT-DP-02: Predictor is added in place with the expected key\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A small dataset exists with event/stimulus metadata, and a registered predictor descriptor has \texttt{code.key="acoustic\_envelop"}.

\textbf{Input:} \texttt{add\_predictor(ds, code, filter\_x=False, y="meg")}.

\textbf{Output:} The function returns \texttt{None}; \texttt{ds} contains a new \texttt{acoustic\_envelop} predictor column aligned with the response time axis.

\textbf{Test Case Derivation:} The MIS specifies that \texttt{add\_predictor} updates the dataset in place and uses \texttt{code.key} as the predictor column name.

\textbf{How Test Will Be Performed:} Use a small dataset fixture and a mocked predictor loader. Assert that the return value is \texttt{None}, the expected key is present, and the predictor length/time axis is compatible with the response.

\item{UT-DP-03: Undefined predictor is rejected\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A dataset exists, but the requested predictor code is not registered.

\textbf{Input:} \texttt{add\_predictor(ds, code="unknown\_predictor", filter\_x=False, y="meg")}.

\textbf{Output:} A documented undefined-predictor error or \texttt{ValueError} is raised.

\textbf{Test Case Derivation:} The MIS lists undefined predictor errors as exception cases for \texttt{add\_predictor}.

\textbf{How Test Will Be Performed:} Call \texttt{add\_predictor} with an unregistered predictor key and assert that execution fails before a predictor column is added.

\end{enumerate}

\subsubsection{M3: Estimator Resolution Module}

The Estimator Resolution Module is specified in the Estimator Resolution Module section of the MIS. Unit tests for this module are high priority because the estimator resolver is the main integration mechanism that routes different estimator choices to different analysis methods.

\begin{enumerate}

\item{UT-ER-01: Valid estimator key resolves to estimator object\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A test experiment defines an estimator registry containing \texttt{"boosting"} mapped to \texttt{BoostingEstimator(...)} and \texttt{"ncrf"} mapped to \texttt{NCRFEstimator(...)}.

\textbf{Input:} \texttt{\_resolve\_estimator("ncrf")}.

\textbf{Output:} The corresponding \texttt{NCRFEstimator} instance is returned.

\textbf{Test Case Derivation:} The MIS states that string estimator keys are resolved through the experiment estimator dictionary.

\textbf{How Test Will Be Performed:} Instantiate a small test experiment with a registry and assert object identity or estimator type for \texttt{"boosting"} and \texttt{"ncrf"}.

\item{UT-ER-02: Missing estimator key raises clear error\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A test experiment defines an estimator registry that does not include \texttt{"unknown"}.

\textbf{Input:} \texttt{\_resolve\_estimator("unknown")}.

\textbf{Output:} \texttt{ValueError} is raised and the message identifies the invalid estimator key or supported options.

\textbf{Test Case Derivation:} The MIS lists \texttt{ValueError} for an estimator key not found in \texttt{estimators}.

\textbf{How Test Will Be Performed:} Use \texttt{pytest.raises(ValueError)} and assert that the error message includes \texttt{"unknown"} or the available estimator keys.

\item{UT-ER-03: Invalid estimator type raises clear error\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A test experiment is available.

\textbf{Input:} \texttt{\_resolve\_estimator(object())}.

\textbf{Output:} \texttt{ValueError} is raised because the input is neither \texttt{str}, \texttt{Estimator}, nor \texttt{None}.

\textbf{Test Case Derivation:} The MIS specifies that invalid estimator types are rejected.

\textbf{How Test Will Be Performed:} Pass a plain object and assert \texttt{ValueError}.

\item{UT-ER-04: Estimator options merge into effective TRF options\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A \texttt{BoostingEstimator} or \texttt{NCRFEstimator} is configured with non-default options.

\textbf{Input:} Call the estimator-option merge helper with explicit TRF defaults and the configured estimator.

\textbf{Output:} The effective options contain estimator-specific values needed by the backend fitter.

\textbf{Test Case Derivation:} The MIS local-function description requires estimator defaults and explicit user options to be merged into effective TRF options.

\textbf{How Test Will Be Performed:} Assert that boosting options such as \texttt{basis}, \texttt{partitions}, and \texttt{error}, or NCRF options such as \texttt{mu} and \texttt{n\_iter}, appear in the effective option dictionary.

\end{enumerate}

\subsubsection{M4: TRF Computation Module}

The TRF Computation Module is specified in the TRF Computation Module section of the MIS. Unit tests for this module verify behavior at the dispatch boundary. The tests should not run the expensive scientific fitting routines; instead, they should mock \texttt{boosting} and \texttt{fit\_ncrf} and assert that the correct callable is constructed or invoked.

\begin{enumerate}

\item{UT-TC-01: \texttt{load\_trf} returns cache path when \texttt{path\_only=True}\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A test experiment can resolve a TRF cache path for a fixed model and estimator configuration.

\textbf{Input:} \texttt{load\_trf("acoustic\_envelop", tstart=0, tstop=0.5, estimator="ncrf", path\_only=True)}.

\textbf{Output:} A filesystem path string is returned; no fitting job is executed.

\textbf{Test Case Derivation:} The MIS specifies that \texttt{load\_trf} returns the cache path when \texttt{path\_only=True}.

\textbf{How Test Will Be Performed:} Mock the fitting job and assert it is not called. Assert that the returned path ends in the expected cache-file extension.

\item{UT-TC-02: Cache miss with \texttt{make=False} raises \texttt{IOError}\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} The resolved TRF cache file does not exist.

\textbf{Input:} \texttt{load\_trf(..., make=False, path\_only=False)}.

\textbf{Output:} \texttt{IOError} is raised.

\textbf{Test Case Derivation:} The MIS lists \texttt{IOError} for a cache miss when \texttt{make=False}.

\textbf{How Test Will Be Performed:} Use a temporary cache directory with no TRF file and assert \texttt{IOError}.

\item{UT-TC-03: Boosting estimator dispatches to boosting analysis path\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} Epoch and predictor fixtures are available, and backend fitting functions are mocked.

\textbf{Input:} \texttt{\_trf\_job(..., estimator=BoostingEstimator(...))}.

\textbf{Output:} A deferred callable is created for the boosting fitting path with boosting-specific options.

\textbf{Test Case Derivation:} The MIS specifies that one branch of \texttt{\_trf\_job} constructs \texttt{partial(boosting, ...)}.

\textbf{How Test Will Be Performed:} Mock \texttt{boosting}; inspect the returned \texttt{partial} or execute it against a mock and assert that boosting arguments such as \texttt{basis} and \texttt{partitions} are passed.

\item{UT-TC-04: NCRF estimator dispatches to NCRF analysis path\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} Epoch, predictor, forward-model, and covariance fixtures are available as lightweight stubs; \texttt{fit\_ncrf} is mocked.

\textbf{Input:} \texttt{\_trf\_job(..., estimator=NCRFEstimator(mu=0.1, n\_iter=100))}.

\textbf{Output:} A deferred callable is created for the NCRF fitting path with NCRF-specific options.

\textbf{Test Case Derivation:} The MIS specifies that the NCRF branch constructs \texttt{partial(fit\_ncrf, ...)} and includes estimator-specific NCRF options.

\textbf{How Test Will Be Performed:} Mock \texttt{fit\_ncrf}; inspect the returned callable or execute it against stubs and assert that \texttt{mu}, \texttt{n\_iter}, \texttt{normalize}, and \texttt{in\_place} are passed.

\item{UT-TC-05: Backward model with multiple predictors is rejected\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A model expression contains more than one predictor term.

\textbf{Input:} \texttt{\_trf\_job(..., x="x1+x2", backward=True)}.

\textbf{Output:} \texttt{ValueError} is raised.

\textbf{Test Case Derivation:} The MIS lists \texttt{ValueError} for backward models with multiple predictors.

\textbf{How Test Will Be Performed:} Use a model fixture with two predictor terms and assert \texttt{ValueError}.

\end{enumerate}

\subsection{Tests for Nonfunctional Requirements}

Unit-level nonfunctional testing focuses on maintainability and reproducibility of the integration boundary. Full performance and cross-platform testing remain system-level concerns.

\begin{enumerate}

\item{UT-NFR-MAINT-01: Estimator addition is localized\\}

\textbf{Type:} Static, manual/automatic review.

\textbf{Initial State:} Estimator classes, estimator registry, and \texttt{TRFExperiment} dispatch code are available.

\textbf{Input/Condition:} Inspect the files implementing \texttt{Estimator}, \texttt{BoostingEstimator}, \texttt{NCRFEstimator}, and estimator dispatch.

\textbf{Output/Result:} Adding or modifying an estimator should require changes to the estimator strategy class and registry, not unrelated preprocessing or raw-data loading code.

\textbf{How Test Will Be Performed:} Use code review and optional import-level tests to confirm that estimator classes can be imported independently and that the resolver accepts new estimator objects through the documented strategy interface.

\item{UT-NFR-REP-01: Cache path is deterministic for fixed options\\}

\textbf{Type:} Functional, dynamic, automatic.

\textbf{Initial State:} A test experiment has fixed subject, epoch, predictor, estimator, and TRF options.

\textbf{Input/Condition:} Call \texttt{load\_trf(..., path\_only=True)} twice with identical arguments.

\textbf{Output/Result:} Both calls return the same path.

\textbf{How Test Will Be Performed:} Use a temporary cache directory and assert path equality. A companion test should change an estimator-relevant option and assert that the path or cache metadata changes accordingly.

\end{enumerate}

\subsection{Traceability Between Test Cases and Modules}

\begin{table}[h!]
\centering
\begin{tabularx}{\textwidth}{p{0.25\textwidth}X}
\toprule
\textbf{Module} & \textbf{Unit Test Cases} \\
\midrule
M1 Data Loading Module & UT-DL-01, UT-DL-02, UT-DL-03 \\
M2 Data Preprocessing Module & UT-DP-01, UT-DP-02, UT-DP-03 \\
M3 Estimator Resolution Module & UT-ER-01, UT-ER-02, UT-ER-03, UT-ER-04 \\
M4 TRF Computation Module & UT-TC-01, UT-TC-02, UT-TC-03, UT-TC-04, UT-TC-05 \\
Nonfunctional unit-level checks & UT-NFR-MAINT-01, UT-NFR-REP-01 \\
\bottomrule
\end{tabularx}
\caption{Traceability Between Unit Test Cases and Modules}
\label{tab:unit-module-trace}
\end{table}

\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\newpage

\section{Appendix}

This is where you can place additional information.

\subsection{Symbolic Parameters}

The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
Their values are defined in this section for easy maintenance.

\subsection{Usability Survey Questions?}

\wss{This is a section that would be appropriate for some projects.}

\end{document}
